\cvsection{Summary}
\textbf{A skilled multi-tasker passionate about Cyber-Physical Systems, Embedded Systems and Internet of Things. \\Looking for opportunities to hone my skills to ensure my professional growth and benefit the organization}

\cvsection{Education}
\cveventsidebar{Bachelor degree}{National Institute of Engineering}{Aug 2016 -- May 2020}{Mysore, India}
\begin{itemize}
\item Major: Electronics \& Communication
\smallskip
\item CGPA: 9.05 (6 semesters)
% \smallskip
% \item Related coursework:\\  Probability, Introduction to Algorithms, Operating Systems, \\ Object Oriented Programming, Discrete Math,  Database,\\ Principles of Programming Languages, Data Structures,\\ Introduction to Computer Network, System Programming, \\ Artificial Intelligence, Computer Architecture, Digital Logic
\end{itemize}


\cvsection{Projects}

\cvproject{FreeRTOS Projects}
\begin{itemize}
\item Implemetation of various features of FreeRTOS on ESP32 microcontroller.
\smallskip
\item \color{blue}{\href{https://github.com/shashank-simha/FreeRTOS-Projects}{github.com/shashank-simha/RTOS-Projects}}
\smallskip\smallskip
\end{itemize}

\cvproject{NIE Summer of Code (Projects on ESP 32)}
\begin{itemize}
\item Web server, Bluetooth SD card reader, Remote Temperature logger, OTA, Web Client, etc. implementation on ESP32.
\smallskip
\item \color{blue}{\href{https://github.com/shashank-simha/NSoC5.0}{github.com/shashank-simha/NSoC5.0}}
\smallskip\smallskip
\end{itemize}

\cvproject{Presenter}
\begin{itemize}
\item Android app for remotely controlling presentations built using RevealJS (Integrated with Google Firebase).
\smallskip
\item \color{blue}{\href{https://github.com/shashank-simha/Presenter}{github.com/shashank-simha/Presenter}}
\smallskip\smallskip
\end{itemize}

\cvproject{ECG Data Reduction Algorithms}
\begin{itemize}
\item Implementation of AZTEC, TP and DCT algorithms for reducing the size of ECG data.
\smallskip
\item \color{blue}{\href{https://github.com/shashank-simha/ECG-Compression}{github.com/shashank-simha/ECG-Compression}}
\smallskip\smallskip
\end{itemize}


\cvsection{Achievements}

\cvproject{Best Website Award}
\begin{itemize}
\item AISYWC'18.
\end{itemize}

\cvproject{Secured state wise 2nd rank}
\begin{itemize}
\item National Means cum Merit Scholarship Exam (2011).
\end{itemize}

\cvsection{Activities}

\begin{itemize}
\item Cadet - National Cadet Corps (NCC)
\item State level Swimmer
\end{itemize}
