% \cvsection{Referees}

% % \cvref{name}{email}{mailing address}
% \cvref{Prof.\ Alpha Beta}{a.beta@university.edu}
% {Address Line 1\\Address line 2}

% \divider

% \cvref{Prof.\ Gamma Delta}{g.delta@university.edu}
% {Address Line 1\\Address line 2}


\cvsection{Honors \& Awards}
\cvevent{}{International Mathematical Olympiad (IMO)}{July 2016}{Hong-Kong}
\begin{itemize}
\item Bronze Medal
\item IMO is the most important olympiad for high school students in mathematics. Number of participating
countries is more than 100 and number of contestants is more than 600.
\end{itemize} 
\cvevent{}{Balkan Mathematical Olympiad (BMO)}{May 2016}{Tirana, Albania}
\begin{itemize}
\item Silver Medal
\item BMO is olympiad for countries placed in Balkan peninsula and with several guest  countries. Number of participating countries more than 20 and each country has their top 6 contestants.
\end{itemize} 
\cvevent{}{National Olympiads in Mathematics}{March 2016}{Kokshetau, Kazakhstan}
\begin{itemize}
\item Absolute Winner 2016
\end{itemize}
\cvevent{}{International Zhautykov Olympiad (IZhO)}{January 2015}{Almaty, Kazakhstan}
\begin{itemize}
\item Silver Medal
\end{itemize}


\cvsection{Activities}
\cvevent{Jury Member}{International Zhautykov Olympiad (IZhO)}{January 2017-2019}{Almaty, Kazakhstan}
\begin{itemize}
\item IZhO is internation olympiad in physics, \\ math and computer science with number of  \\ participating countries 20. I was a jury member in IZhO in math section three times.
\end{itemize}
\smallskip
\cvevent{Volunteer}{Winter Universiade}{February 2017}{Almaty, Kazakhstan}
\begin{itemize}
\item Universiade is a competition of students from all over the world in various of winter sports.\\ I volunteered as an attache of Brazil.
\end{itemize}
\smallskip
\cvevent{Volunteer}{Almaty ASTC Sprint Triathlon Cup}{August 2018}{Almaty, Kazakhstan}
\begin{itemize}
\item Triathlon is a competition where participants compete in
3 types of sport - swimming, cycling and running. I volunteered as a member of \\arrival and departure team.
\end{itemize}


%  \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
%  \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
%  \divider
%  \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% \divider
%  \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% \divider
%  \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}